---
title: "Diamonds"
author: "Awatef Alshehri"
date: "1/20/2022"
output: html_document
---

## Diamonds

### Step 1: Installing the tidyverse packages

```{r}
install.packages("tidyverse")  # This package is common and used in data analysis.

```

```{r diamond}

library(tidyverse)
# https://www.tidyverse.org/packages/

```

#### Core tidyverse:

-   ggplot2 : used for data visualization.
-   tidyr : used to get to tidy data (data with a consistent form).
-   dplyr : used for data manipulation.
-   readr : used to read rectangular data (like csv, tsv, and fwf)
-   Purrr : used to replace many "for loops" with code that is easier to write and more expressive.
-   stringr : used for strings manipulation as easy as possible.
-   forcats : used to solve common problems with factors

------------------------------------------------------------------------

-   Step 2: Exploring the Dataset

```{r diamond}
Diam = diamonds   # identify the dataset
```

```{r diamond}
# To view the structure of the "diamonds" dataset

str(Diam)
```

```{r diamond}
# To view the top rows of "diamonds" dataset.

head(Diam)

```

```{r diamond}
# To view column names from diamond dataset

colnames(Diam)

```

```{r diamond}
#EDA 

dim(Diam)

# To have a view of the dataset structure

glimpse(Diam) 

```

### Step 3: Cleaning Data

```{r diamond}

summary(Diam)

```

```{r diamond}

summarize(Diam, mean_carat = mean(carat))

```

### Step 4: Visualizing Data

#### A) Point plot:

```{r diamond}

ggplot(data = Diam, aes(x=carat, y = price, color = cut)) +
  geom_point()

```

```{r diamond}

ggplot(data = Diam, aes(x=depth, y = price, color = cut)) +
  geom_point()

```

#### B) Histograms plot:

```{r diamond}

ggplot(Diam, aes(price, fill = clarity)) +
  geom_histogram(bins = 30)
```

```{r diamond}

ggplot(Diam, aes(price, fill = color)) + 
  geom_histogram(binwidth = 30) + 
  facet_wrap(~ clarity, scale = "free_y")
```

#### C) Bar plot:

```{r diamond}
ggplot(data=Diam)+
  geom_bar(mapping = aes(x=cut , fill=cut))
```

```{r diamond}
# we creat stacked bar charts showing different classes

ggplot(data = Diam)+geom_bar(mapping=aes(x=cut,fill=clarity))
```
